Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-07 talk/icooolps2011/paper.tex
add a comment
s/fancy/advanced/

@@

As the running example of this paper we will use a very simple and bare-bones
object model that just supports classes and instances, without any
inheritance or other fancy features. The model has classes, which contain methods.
Instances have a class. Instances have their own attributes (or fields). When looking up an
attribute on an instance, the instances attributes are searched. If the
attribute is not found there, the class' methods are searched.

>>>>

XXX [fijal] yet another advantage is that JIT is by design supporting the whole
    language

@@

As the running example of this paper we will use a very simple and bare-bones
object model that just supports classes and instances, without any
inheritance or other advanced features. The model has classes, which contain methods.
Instances have a class. Instances have their own attributes (or fields). When looking up an
attribute on an instance, the instances attributes are searched. If the
attribute is not found there, the class' methods are searched.
